Automatic Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Handlebar Perturbations\\Version 2.dev

### 2024-10-03 main.tex
Slight correction to Marten's equations.

To illustrate the effect of the balance assist system on fall probability, we
will give an example of how the data collected during the experiments is used
to predict fall probability. We use Equation~\ref{eq:log-regress} and the
coefficients in Table~\ref{tab:freq-coefs-6}. For simplicity's sake, the
interaction effects are not included. For example, assuming that the mean
angular impulse $\bar{L}$ of all the perturbations applied to a participant is
100~\si{\newton} and the standard deviation $\sigma_{L}=15$. The centered and
scaled angular impulse can be calculated by subtracting $\bar{L}$ from the
applied angular impulse $L$, and dividing this by $\sigma_{L}$. The same
applies for the perturbation order $j$, initial roll angle $\phi_0$, and
initial steer angle $\delta_0$. If we take the coefficients estimated for
cycling at 6~\si{\kph}, the log-odds of falling can be calculated as follows:
\todo{Check this equation, where is \(\bar{L}\) 100N in the equation?}
%
\begin{equation}
  \begin{split}
    \log \left( \frac{p_{ij}}{1-p_{ij}} \right)
    = & \quad
    \beta + \sum_{k=1}^{k=5}\alpha_k \frac{x_{ij}^{k}-\bar{x}_{ij}^{k}}{\sigma^{x^{k}}} \\
    = &
   -0.29 + 1.69\cdot\frac{110~\si{\newton} - 100\si{\newton}}{15\si{\newton}} -0.77\cdot\frac{10-20}{11.54}  \\
    & -0.25\cdot\frac{-6\si{\degree}-2\si{\degree}}{10\si{\degree}}
    -0.14\cdot\frac{1\si{\degree}+3\si{\degree}}{5\si{\degree}} -0.64\cdot s \\
    = &
    1.59 -0.64 \cdot s
  \end{split}
  \textrm{.}
\end{equation}
%
The state of the balance assist \(s\) is a binary variable. If the
balance assist is turned on, the log-odds that a fall occurs are decreased by
0.64. The odds and probability can be calculated:
%
\begin{align}
  \frac{p_{ij}}{1-p_{ij}} & = e^{1.59-0.64c} =
  e^{1.59}\cdot e^{-0.64s} = 4.90 \cdot 0.53c \\
  p_{ij}|_{c=0} & = \frac{4.90}{1 + 4.90} = 0.83 \\
  p_{ij}|_{c=1} & = \frac{4.90\cdot0.53}{1 + 4.90\cdot{0.53}} = 0.72
\end{align}
%
Turning on the balance assist system reduces the probability that the
perturbation results in a fall from 83\% to 72\% in this case.

@@

\section*{Funding}
%
This study is funded by Dutch Research Council, Nederlandse Organisatie voor
Wetenschappelijk Onderzoek (NWO), under the Citius Altius Sanius program and in
collaboration with Bosch eBike Systems and Royal Dutch Gazelle. The funders had
no role in the data collection and analysis or preparation of the manuscript.

>>>>

To illustrate the effect of the balance assist system on fall probability, we
will give an example of how the data collected during the experiments is used
to predict fall probability. We use Equation~\ref{eq:log-regress} and the
coefficients in Table~\ref{tab:freq-coefs-6}. For simplicity's sake, the
interaction effects are not included. For example, assuming that the mean
angular impulse $\bar{L}$ of all the perturbations applied to a participant is
100~\si{\newton} and the standard deviation $\sigma_{L}=15$. The centered and
scaled angular impulse can be calculated by subtracting $\bar{L}$ from the
applied angular impulse $L$, and dividing this by $\sigma_{L}$. The same
applies for the perturbation order $j$, initial roll angle $\phi_0$, and
initial steer angle $\delta_0$. If we take the coefficients estimated for
cycling at 6~\si{\kph} and example means, the log-odds of falling can be
calculated as follows:
%
\begin{equation}
  \begin{split}
    \log \left( \frac{p_{ij}}{1-p_{ij}} \right)
    = & \quad
    \beta + \sum_{k=1}^{k=5}\alpha_k \frac{x_{ij}^{k}-\bar{x}_{ij}^{k}}{\sigma^{x^{k}}} \\
    = &
   -0.29 + 1.69\cdot\frac{110~\si{\newton} - 100\si{\newton}}{15\si{\newton}} -0.77\cdot\frac{10-20}{11.54}  \\
    & -0.25\cdot\frac{-6\si{\degree}-2\si{\degree}}{10\si{\degree}}
    -0.14\cdot\frac{1\si{\degree}+3\si{\degree}}{5\si{\degree}} -0.64 s \\
    = &
    1.59 -0.64 s
  \textrm{.}
  \end{split}
\end{equation}
%
The state of the balance assist \(s\) is a binary variable. If the
balance assist is turned on, the log-odds that a fall occurs are decreased by
0.64. The odds and probability can be calculated:
%
\begin{align}
  \frac{p_{ij}}{1-p_{ij}} & = e^{1.59-0.64s} =
  e^{1.59}\cdot e^{-0.64s} = 4.90 \cdot e^{-0.64s} \\
  p_{ij}|_{s=0} & = \frac{4.90}{1 + 4.90} = 0.83 \\
  p_{ij}|_{s=1} & = \frac{4.90\cdot0.53}{1 + 4.90\cdot{0.53}} = 0.72
\end{align}
%
Turning on the balance assist system reduces the probability that the
perturbation results in a fall from 83\% to 72\% in this case.

@@

\section*{Funding}
%
This study is funded by Dutch Research Council, Nederlandse Organisatie voor
Wetenschappelijk Onderzoek (NWO), under the Citius Altius Sanius Perspectief
program and in collaboration with Bosch eBike Systems and Royal Dutch Gazelle.
The funders had no role in the data collection and analysis or preparation of
the manuscript.
